The Ranked Nearest Neighbour Interchange space

### 2019-08-14 paper.tex
minor on diameter section

With the results of Section~\ref{section:caterpillar_convex} we can easily provide the exact diameter of the $\rnni$ graph and hence, improve the bounds for the diameter given in \autocite{Gavryushkin2018-ol}.
Moreover, we can conclude from Lemma~\ref{lemma:caterpillar_diameter} that the maximum distance computed by algorithm $\findpath$, which was dicussed introduced above, equals the diameter of $\rnni$.
This suggests that it gives reasonable estimates of distances.
For further details on the quality of that algorithm we refer the reader to Section~\ref{section:computation}.

@@

\begin{proof}
	Let $T = (( \dots (n,1)2)\dots)n-1)$ and $R = (( \dots (n,n-1)n-2)\dots)1)$.
    According to Theorem~\ref{thm:caterpillar_convex}, there is a shortest path between $T$ and $R$ that is a caterpillar path.
    We can compute a shortest caterpillar path by using $\csort$ as explained above.
    When running this algorithm on $T$ and $R$, taxon $i$ swaps $n-1-i$ times with its right neighbour.
    Therefore, the length of a shortest caterpillar path is $\sum\limits_{i=1}^{n-1}(n-1-i) = \sum\limits_{i=0}^{n-2}i = \frac{(n-1)(n-2)}{2}$.
\end{proof}

>>>>

With the results of Section~\ref{section:caterpillar_convex} we can easily provide the exact diameter of the $\rnni$ graph and hence improve the bounds for the diameter given in \autocite{Gavryushkin2018-ol}.
Moreover, we can conclude from Lemma~\ref{lemma:caterpillar_diameter} that the maximum distance computed by algorithm $\findpath$, introduced in Section~\ref{section:geometry}, equals the diameter of $\rnni$.
This suggests that this algorithm computes reasonable estimates of distances.
For further details on $\findpath$ we refer the reader to Section~\ref{section:computation}.

@@

\begin{proof}
	Let $T = (( \dots (n,1)2)\dots)n-1)$ and $R = (( \dots (n,n-1)n-2)\dots)1)$.
    According to Theorem~\ref{thm:caterpillar_convex}, there is a shortest path between $T$ and $R$ that is a caterpillar path.
    We can compute a shortest caterpillar path by using $\csort$ as explained in Section~\ref{section:caterpillar_convex}.
    When running this algorithm on $T$ and $R$, each taxon $i$ ($i \in \{1, \ldots, n\}$) swaps $n-1-i$ times with its right neighbour.
    Therefore, the length of a shortest caterpillar path is $\sum\limits_{i=1}^{n-1}(n-1-i) = \sum\limits_{i=0}^{n-2}i = \frac{(n-1)(n-2)}{2}$.
\end{proof}
